

<h1> Exploratory Data Analysis</h1>
<p> Here we look through a  plane crashes dataset available on Kaggle. How many plane crashes occurred per year? How about the overall monthly trend? What were the brand of aircrafts involved? How many crashes took place in each a every country since 1908?</p>



<h2> Loading the library </h2>
```{r}
require(dplyr)
require(ggplot2)
require(data.table)
require(formattable)

```



<h3>What is the data made of? What are the variables? </h3>


```{r}
crash <- read.csv('C:/Users/Adhokshaja/Documents/crashes.txt')
dim(crash)
summary(crash)
names(crash)

```


<h2>Convert the dates and extract the Months and the Years</h2>
```{r}
crash$Date <- as.POSIXct(crash$Date,format='%m/%d/%Y')
crash$Year <- year(crash$Date)
crash$Month <- month(crash$Date)
```

<h2>How many plane crashes took place by year?</h2>

```{r}
temp <- crash %>% group_by(Year)%>% summarise(n=n())
ggplot(data=temp,aes(x=Year,y=n))+geom_bar(stat='identity')+xlab('Years')+ylab('Count')
```

<h2>How many plane crashes take place by month?</h2>
```{r}
temp <- crash %>% group_by(Month) %>% summarise(n=n())
ggplot(data=temp,aes(x=as.factor(Month),y=n))+geom_bar(stat='identity')+xlab('Months')+ylab('Count')

```


<h2>Civilian VS Military Proportions</h2>

```{r}
temp <- crash
temp$Operator <- as.character(temp$Operator)
temp$Operator <- ifelse(temp$Operator=='',NA,temp$Operator)
temp <- temp %>% mutate(crash_type=ifelse(grepl('\\bMilitary\\b',Operator),'Military','Civilian'))
temp<- temp %>% select(Year,Operator,crash_type)
ggplot(data = temp, aes(x = (Year),fill=crash_type)) +
  geom_bar(position = 'fill')+xlab('Year')+ylab('Proportions')+ggtitle('Proportions of civilian and military plane crashes')
```
<p>As seen in the above plot the proportion of military crashes seem to be more in the year before 1950. This could be attributed to
the world war.</p>

<h2>Top 30 companies by number of crashes</h2>

```{r}
temp <- crash
temp$Type <- as.character(temp$Type)
temp$company <- temp$Type
temp$company <- ifelse(temp$company=='',NA,temp$company)
temp<- na.omit(temp)
temp <- temp %>% mutate(company=ifelse(grepl('\\bBoeing\\b',company),'Boeing',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bBell\\b',company),'Bell',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bCessna\\b',company),'Cessna',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bGrumman\\b',company),'Grumman',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bMcDonnell\\b',company),'McDonnell',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bBeechcraft\\b',company),'Beechcraft',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bMi\\b',company),'Mi',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bAntonov\\b',company),'Antonov',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bAirbus\\b',company),'Airbus',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bBAe\\b',company),'British Aerospace',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bde Havilland Canada\\b',company),'de Havilland Canada',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bde Havilland\\b',company),'de Havilland',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bDe Havilland\\b',company),'de Havilland',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bLearjet\\b',company),'Learjet',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bAerospatiale\\b',company),'Aerospatiale',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bIlyushin\\b',company),'Ilyushin',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bPilatus\\b',company),'Pilatus',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bIlysushin\\b',company),'Ilysushin',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bSikorsky\\b',company),'Sikorsky',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bFokker\\b',company),'Fokker',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bDouglas\\b',company),'Douglas',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bConvair\\b',company),'Convair',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bEurocopter\\b',company),'Eurocopter',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bCASA\\b',company),'CASA',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bLet\\b',company),'Let',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bPiper\\b',company),'Piper',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bPilatus\\b',company),'Pilatus',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bLockheed\\b',company),'Lockheed',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bBombardier\\b',company),'Bombardier',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bBritten-Norman\\b',company),'Britten-Norman',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bBandeirante\\b',company),'Bandeirante',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bRockwell\\b',company),'Rockwell',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bAero Commander\\b',company),'Aero Commander',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bAerostar\\b',company),'Aerostar',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bAgusta\\b',company),'Agusta',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bZeppelin\\b',company),'Zeppelin',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bYunshuji\\b',company),'Yunshuji',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bVickers\\b',company),'Vickers',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bVolpar\\b',company),'Volpar',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bAirbusA310-304\\b',company),'Airbus',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bCurtiss\\b',company),'Curtiss',company))
temp <- temp %>% mutate(company=ifelse(grepl('\\bTupolev\\b',company),'Tupolev',company))


temp <- temp %>% group_by(company) %>% summarise(n =n())
temp <- temp %>% arrange(desc(n))
temp %>%
    top_n(30, n) ->
    top_30

top_30 %>%
    arrange(desc(n)) %>%
    formattable(list(n = color_bar("orange")), align = 'l')
```
<h2> How do the ratio of fatalities to the number of people aboard differ by year?</h2>
```{r}
temp <- crash %>% mutate(ratio=Fatalities/Aboard)
temp <- temp %>% group_by(Year) %>% summarise(m=mean(ratio,na.rm=T))
temp <- temp %>% select(Year,m)
ggplot(data=temp,aes(x=(Year),y=m))+geom_bar(stat='identity')+xlab('Years')+ylab('Ratio')

   
```
<p> We see that the overall trend in the ratio is decreasing gradually.</p>
<h2> Generating a world map colored with the frequency of plane crashes color coded .</h2>
```{r}
temp <- crash
temp$loc_new <- crash$Location
temp$loc_new <- as.character(temp$loc_new)
temp$loc_new <- ifelse(temp$loc_new=='',NA,temp$loc_new)
temp <- na.omit(temp)
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bVenezuela\\b',loc_new),'Venezuela',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bCanada\\b',loc_new),'Canada',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bNetherlands\\b',loc_new),'Netherlands',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bBrazil\\b',loc_new),'Brazil',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bIndia\\b',loc_new),'India',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bChile\\b',loc_new),'Chile',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bUganda\\b',loc_new),'Uganda',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bJapan\\b',loc_new),'Japan',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bFrance\\b',loc_new),'France',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bItaly\\b',loc_new),'Italy',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bTanzania\\b',loc_new),'Tanzania',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bEcuador\\b',loc_new),'Ecuador',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bKyrgyzstan\\b',loc_new),'Kyrgyzstan',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bUnited Arab Emirates\\b',loc_new),'United Arab Emirates',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bRussia\\b',loc_new),'Russia',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bIndonesia\\b',loc_new),'Indonesia',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bSomalia\\b',loc_new),'Somalia',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bMexico\\b',loc_new),'Mexico',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bGuatemala\\b',loc_new),'Guatemala',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bColombia\\b',loc_new),'Colombia',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bSudan\\b',loc_new),'Sudan',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bAustralia\\b',loc_new),'Australia',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bNigeria\\b',loc_new),'Nigeria',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bPanama\\b',loc_new),'Panama',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bNepal\\b',loc_new),'Nepal',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bPoland\\b',loc_new),'Poland',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bUkraine\\b',loc_new),'Ukraine',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bDemocratiRepubliCongo\\b',loc_new),'DemocratiRepubliCongo',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bThailand\\b',loc_new),'Thailand',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bEthiopia\\b',loc_new),'Ethiopia',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bPeru\\b',loc_new),'Peru',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bMongolia\\b',loc_new),'Mongolia',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bCongo\\b',loc_new),'Congo',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bNorway\\b',loc_new),'Norway',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bGermany\\b',loc_new),'Germany',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bPakistan\\b',loc_new),'Pakistan',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bIran\\b',loc_new),'Iran',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bIraq\\b',loc_new),'Iraq',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bAfghanistan\\b',loc_new),'Afghanistan',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bNapal\\b',loc_new),'Nepal',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bBolivia\\b',loc_new),'Bolivia',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bHungary\\b',loc_new),'Hungary',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bAzerbaijan\\b',loc_new),'Azerbaijan',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bAlbania\\b',loc_new),'Albania',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bUnited Kingdom\\b',loc_new),'UK',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bSaudi Arabia\\b',loc_new),'Saudi Arabia',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bChina\\b',loc_new),'China',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bPapua New Guinea\\b',loc_new),'Papua New Guinea',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bGabon\\b',loc_new),'Gabon',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bKenya\\b',loc_new),'Kenya',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bKazakhstan\\b',loc_new),'Kazakhstan',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bEgypt\\b',loc_new),'Egypt',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bNew Zealand\\b',loc_new),'New Zealand',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bHaiti\\b',loc_new),'Haiti',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bKenya\\b',loc_new),'Kenya',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bBahamas\\b',loc_new),'Bahamas',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bAlgeria\\b',loc_new),'Algeria',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bNamibia\\b',loc_new),'Namibia',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bTurkey\\b',loc_new),'Turkey',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bEstonia\\b',loc_new),'Estonia',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bPhilippines\\b',loc_new),'Philippines',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bLuxembourg\\b',loc_new),'Luxembourg',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bTaiwan\\b',loc_new),'Taiwan',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bCameroon\\b',loc_new),'Cameroon',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bChad\\b',loc_new),'Chad',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bAngola\\b',loc_new),'Angola',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bSwitzerland\\b',loc_new),'Switzerland',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bRussian\\b',loc_new),'Russia',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bIvory Coast\\b',loc_new),'Ivory Coast',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bGhana\\b',loc_new),'Ghana',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bSwitzerland\\b',loc_new),'Switzerland',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bSpain\\b',loc_new),'Spain',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bArgentina\\b',loc_new),'Argentina',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bArmenia\\b',loc_new),'Armenia',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bBurma\\b',loc_new),'Myanmar',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bMyanmar\\b',loc_new),'Myanmar',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bPhilipines\\b',loc_new),'Philipines',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bBelgium\\b',loc_new),'Belgium',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bCalifornia\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bTexas\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bIowa\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bNew York\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bAlaska\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bNevada\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bWisconsin\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bMinnesota\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bWyoming\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bMichigan\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bCalifornia\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bOhio\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bVermont\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bPuerto Rico\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bMontana\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bArizona\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bHawaii\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bWashington\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bOregon\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bIllinois\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bDakota\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bLouisiana\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bPennsylvania\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bColorado\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bWake\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bSouth Africa\\b',loc_new),'South Africa',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bMalawi\\b',loc_new),'Malawi',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bLaos\\b',loc_new),'Laos',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bAK\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bNew Hampshire\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bCarolina\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bNew Jersey\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bVirginia\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bRhode Island\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bIndiana\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bGeorgia\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bManitoba\\b',loc_new),'Canada',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bBulgaria\\b',loc_new),'Bulgaria',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bVietnam\\b',loc_new),'Vietnam',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bConnecticut\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bBritish Columbia\\b',loc_new),'Canada',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bKentucky\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bKansas\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bWisconson\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bArkansas\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bUnited States\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bMissouri\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bTennessee\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bUSSR\\b',loc_new),'Russia',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bUzbekistan\\b',loc_new),'Uzbekistan',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bNebraska\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bTrinidad\\b',loc_new),'Trinidad',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bEngland\\b',loc_new),'UK',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bNewfoundland\\b',loc_new),'Canada',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bPortugal\\b',loc_new),'Portugal',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bMali\\b',loc_new),'Mali',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bChina\\b',loc_new),'China',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bMassachusetts\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bGreece\\b',loc_new),'Greece',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bNicaragua\\b',loc_new),'Nicaragua',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bAmerican\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bUK\\b',loc_new),'UK',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bSingapore\\b',loc_new),'Singapore',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bMalaysia\\b',loc_new),'Malaysia',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bSenegal\\b',loc_new),'Senegal',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bYemen\\b',loc_new),'Yemen',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bAlabama\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bUtah\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bIdaho\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bCA\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bCosta Rica\\b',loc_new),'Costa Rica',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bUruguay\\b',loc_new),'Uruguay',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bMozambique\\b',loc_new),'Mozambique',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bOman\\b',loc_new),'Oman',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bRomania\\b',loc_new),'Romania',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bCosta Rica\\b',loc_new),'Costa Rica',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bZimbabwe\\b',loc_new),'Zimbabwe',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bU.S\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bSyria\\b',loc_new),'Syria',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bMorocco\\b',loc_new),'Morocco',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bIceland\\b',loc_new),'Iceland',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bMaine\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bMorocco\\b',loc_new),'Morocco',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bWashingon\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bAmsterdam\\b',loc_new),'Netherlands',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bAustria\\b',loc_new),'Austria',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bVienna\\b',loc_new),'Austria',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bYugoslavia\\b',loc_new),'Yugoslavia',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bGreenland\\b',loc_new),'Greenland',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bMacedonia\\b',loc_new),'Macedonia',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bFrench Equitorial Africa\\b',loc_new),'French Equitorial Africa',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bFiji\\b',loc_new),'Fiji',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bCzechoslovakia\\b',loc_new),'Czechoslovakia',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bHonduras\\b',loc_new),'Honduras',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bEl Salvador\\b',loc_new),'El Salvador',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bDominican Republic\\b',loc_new),'Dominican Republic',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bDenmark\\b',loc_new),'Denmark',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bMississippi\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bCambodia\\b',loc_new),'Cambodia',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bMaryland\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bScotland\\b',loc_new),'UK',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bHati\\b',loc_new),'Haiti',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bNew Guinea\\b',loc_new),'New Guinea',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bMauritania\\b',loc_new),'Mauritania',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bOklahoma\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bTennesee\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bCuba\\b',loc_new),'Cuba',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bSouth Korea\\b',loc_new),'South Korea',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bSweden\\b',loc_new),'Sweden',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bFrench Polynesia\\b',loc_new),'French Polynesia:Tahaa',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bHong Kong\\b',loc_new),'China',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bSri Lanka\\b',loc_new),'Sri Lanka',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bJamaica\\b',loc_new),'Jamaica',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bSierre Leone\\b',loc_new),'Sierra Leone',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bDeleware\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bFrench West Africa\\b',loc_new),'French West Africa',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bNorth Korea\\b',loc_new),'North Korea',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bIsrael\\b',loc_new),'Israel',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bMassachusett\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bDelaware\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bMalagasy Republic\\b',loc_new),'Malagasy Republic',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bMalta\\b',loc_new),'Malta',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bFlorida\\b',loc_new),'USA',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bIreland\\b',loc_new),'Ireland',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bEnglish\\b',loc_new),'UK',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bOkinawa\\b',loc_new),'Japan',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bMalaya\\b',loc_new),'Malaysia',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bWest Indies\\b',loc_new),'West Indies',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bOkinawa\\b',loc_new),'Japan',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bBahrain\\b',loc_new),'Bahrain',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bThiland\\b',loc_new),'Thailand',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bIrish\\b',loc_new),'Ireland',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bBelize\\b',loc_new),'Belize',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bGuam\\b',loc_new),'Guam',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bEquatorial Guinea\\b',loc_new),'Equatorial Guinea',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bSierra Leone\\b',loc_new),'Sierra Leone',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bTunisia\\b',loc_new),'Tunisia',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bLithuania\\b',loc_new),'Lithuania',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bSamoa\\b',loc_new),'Samoa',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bAzores\\b',loc_new),'Azores:Sao Miguel',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bCanary Islands\\b',loc_new),'Spain',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bGuadeloupe\\b',loc_new),'Guadeloupe',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bGibraltar\\b',loc_new),'UK',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bZambia\\b',loc_new),'Zambia',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bChad\\b',loc_new),'Chad',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bRwanda\\b',loc_new),'Rwanda',loc_new))
temp <- temp %>% mutate(loc_new=ifelse(grepl('\\bPoland\\b',loc_new),'Poland',loc_new))
temp <- temp %>% group_by(loc_new) %>% summarise(n=n())
temp <- temp %>% arrange(desc(n))

library(rworldmap)

#create a map-shaped window
mapDevice('x11')
#join to a coarse resolution map
spdf <- joinCountryData2Map(temp, joinCode="NAME", nameJoinColumn="loc_new")

mapCountryData(spdf, nameColumnToPlot="n", catMethod="logFixedWidth")






```

<p>The countries in red are the ones with one of the highest number of total plane crashes throughout history.<p>
<p> We plot a horizontal bar plot for the top 30 countries</p>
```{r}
temp <- temp %>% arrange(desc(n))
temp %>%
    top_n(30, n) ->
    top_30

top_30 %>%
    arrange(desc(n)) %>%
    formattable(list(n = color_bar("yellow")), align = 'l')
rmd2blogger <- function(rmdfile) {
+     
+     stopifnot(require(knitr))
+     
+     ## knit rmdfile to <body> - only html
+     knit2html(rmdfile, fragment.only = TRUE)
+     
+     ## read knitted html file
+     htm.name <- gsub(".Rmd", ".html", rmdfile)
+     tmp <- readLines(htm.name)
+     
+     ## substitue important parts
+     tmp <- gsub("<pre><code class=\"r\">", "<pre class=\"brush: r\">", tmp)
+     tmp <- gsub("</code></pre>", "</pre>", tmp)
+     
+     ## write with .blg file ending
+     writeLines(tmp, paste(htm.name, ".blg", sep =""))
+     
+ }
> rmd2blogger('test.Rmd')
```